%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Aayan Nayak} % Your name
\address{Delhi} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+91)~9911138148 \\ aayan.nayak2001@gmail.com} % Your phone number and email

\begin{document}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{Ernst \& Young }{}{Consultant} {\textnormal{October 2025 - Present}}
\item Found multiple web vulnerabilities like - XSS, Security Misconfigurations, and .
\item Conducted an analysis of recurring security gaps recommending process improvements \& training for dev teams. 
\item Mentored interns/colleagues on secure code review \& vulnerability validation.
    
\begin{rSubsection}{Ernst \& Young }{}{Associate Consultant} {\textnormal{October 2024 - Present}}
\item Took ownership of end-to-end SAST/DAST assessments along with Black Box for multiple applications.
\item Conducted an analysis of recurring security gaps recommending process improvements \& training for dev teams. 
\item Mentored interns/colleagues on secure code review \& vulnerability validation.

{\em Senior Analyst}
\hfill{July 2023 - September 2024}
\item Specialized in triage \& risk-based prioritization of vulnerabilities, reduced false positives by 42\%.
\item Partnered with developers during remediation translated technical findings into business impact
\item Performed ad-hoc security assessments under tight deadline\textbf{s}, ensuring release timelines weren’t blocked.
\item Built dashboards \& reporting frameworks to track vulnerability trends (closure rate, recurring issues).

{\em Senior Analyst Intern}
\hfill{ January 2023 - June 2023}
\item Assisted in secure code reviews (SAST) on .NET/Java apps, learned triaging false positives, identifying common issues. 
\item Conducted DAST scans using tools Burp Suite, validated findings with manual testing.
\item Contributed to documentation \& remediation guidelines for dev teams
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{LG Electronics India Pvt. Ltd.}{06 June 2022 - 01 Aug 2022}{Spring Boot Development - IT Dept F\&A}{}
\item Developed CRUD application using Spring Boot with Tomcat web server and PostgreSQL database as the backend.
\item Used to Azure DevOps Server (TFS) platform for maintaining proper workflow.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Skill Set
%----------------------------------------------------------------------------------------

\begin{rSection}{Skill Set}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  Java, Python, JavaScript. \\
Application Security& SAST/DAST tooling (Checkmarx, Burp, ZAP), Manual secure code review (Java, .NET, Python, JavaScript), Threat modeling, OWASP Top 10.\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

%College\\
{\bf NIIT University} \hfill {\em 2019 - 2023} 
\\ BTech in Computer Science \hfill { Overall CGPA: 8.10/10}
%Senior Secondry \\
\item
{\bf Bal Bhavan Public School} 
\\CBSE (Class XII) 
\hfill {Overall Percentage: 82\%}
%High-School \\
\item
CBSE (Class X) 
\hfill {Overall CGPA: 9.2/10}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\begin{rSubsection}{Analyzing polystore database | Casandra \& PySpark} \hfill{}

\item I implemented various DQL commands on databases like Cassandra and used Pyspark for optimizing the same. 
\item Simulated dataset of various sizes to analyze the performance of standalone Casandra and PySpark
\end{rSubsection}

\begin{rSubsection}
{Password Generator \& Strength Checker| Python \&  JS} \hfill{}

\item I developed a secure password generator implementing customization rules (length, character sets, exclusions) to enforce strong credential policies.
\item Built a credential strength checker leveraging regex patterns and resistance against common attacks.
\end{rSubsection}

\begin{rSubsection}
{iCarpool | Android Studio \& Firebase} \hfill{}

\item Developed mobile application for student transportation scheduling.

\item Project qualified for University Hackathon, NeuraHacks 2.0.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENT 
%----------------------------------------------------------------------------------------

\begin{rSection}{ACHIEVEMENT}

\begin{rSubsection}{Client Extraordinaire}{Feb 2024}{EY}{}
\item Exceeded application assessment and revalidation targets for SAST and DAST testing by handling urgent security assessment on time, ensuring no delivery delays, and building client trust. 
\end{rSubsection}
\end{rSection}

\end{document}
